---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# osn

<!-- badges: start -->
<!-- badges: end -->

The goal of osn is to provide access to OpeSky Network historical data.

## Installation

Once published, you will be able to install the released version of
osn from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("osn")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("espinielli/osn")
```
## Example

The following example shows how to retieve one hour worth of
State Vector data within a bounding box^[40 nautical miles around
EDDF's reference point at E8°34.23',  N50°2.00'] around Frankfurt
airport for an hour interval, 09:00 - 10:00 UTC, on Jan 1, 2019:

```{r example, eval=FALSE}
library(osn)

# EDDF
state_vector(
  session,
  wef_time = "2019-01-01 09:00:00",
  til_time = "2019-01-01 10:00:00",
  bbox = c(7.553013, 49.378819,  9.585482, 50.688044),
  icao24 = NULL
)
#> # A tibble: 108,470 x 17
     time icao24   lat   lon velocity heading vertrate callsign onground alert spi   squawk
    <int> <fct>  <dbl> <dbl>    <dbl>   <dbl>    <dbl> <fct>    <lgl>    <lgl> <lgl> <fct> 
 1 1.55e9 06a063  50.4  7.56     272.    101.        0 QTR006   FALSE    FALSE FALSE 4734  
 2 1.55e9 06a063  50.4  7.56     272.    101.        0 QTR006   FALSE    FALSE FALSE 4734  
 3 1.55e9 06a063  50.4  7.56     272.    101.        0 QTR006   FALSE    FALSE FALSE 4734  
 4 1.55e9 06a063  50.4  7.57     272.    101.        0 QTR006   FALSE    FALSE FALSE 4734  
# … with 108,466 more rows, and 5 more variables: baroaltitude <dbl>, geoaltitude <dbl>,
#   lastposupdate <dbl>, lastcontact <dbl>, hour <int>

```

